Panel Seminars

### 2023-12-05 POP_08_PCA.Rmd
publishing PCA page with all other pages re-knitted so links to PCA page work

---
title: "PCA"
bibliography: DRAFT_PCA/PCA_marineomics.bib
authors: "DL Davenport, KE Lotterhos"
date: "2023-11-07"
output:
  html_document:
    df_print: paged
---

@@

knitr::include_graphics("DRAFT_PCA/Fig.1_Spies_2022_supfig2.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.2_PCAs.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.3_Gompert_Buerkle_fig4.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.4_McVean_fig2.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.5_McVean_fig3.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.6_Lou_Thilk_fig4.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.7_Lou_Thilk_fig6.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.8_Lotterhos2019_fig3.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.9_Yi_Latch_fig2.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.10_Yi_Latch_fig4.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.11_Gompert_Buerkle_fig5.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.12_Morton_fig1.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.13_Novembre_Stephens_fig2.png")

@@

knitr::include_graphics("DRAFT_PCA/Fig.14_McVean_fig5.png")

>>>>

---
title: "PCA"
bibliography: POP_08_PCA_files/PCA_marineomics.bib
authors: "DL Davenport, KE Lotterhos"
date: "2023-12-05"
output:
  html_document:
    df_print: paged
---

@@

knitr::include_graphics("POP_08_PCA_files/Fig.1_Spies_2022_supfig2.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.2_PCAs.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.3_Gompert_Buerkle_fig4.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.4_McVean_fig2.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.5_McVean_fig3.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.6_Lou_Thilk_fig4.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.7_Lou_Thilk_fig6.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.8_Lotterhos2019_fig3.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.9_Yi_Latch_fig2.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.10_Yi_Latch_fig4.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.11_Gompert_Buerkle_fig5.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.12_Morton_fig1.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.13_Novembre_Stephens_fig2.png")

@@

knitr::include_graphics("POP_08_PCA_files/Fig.14_McVean_fig5.png")

### 2023-12-05 index.Rmd
publishing PCA page with all other pages re-knitted so links to PCA page work

* [Choosing a population genomics sequencing approach](POP_01_choosing_population_genetics.html)  
* [Whole Genome Resequencing (WGS)](POP_04_WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](POP_03_poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](POP_05_RDAtraitPredictionTutorial.html)

>>>>

* [Choosing a population genomics sequencing approach](POP_01_choosing_population_genetics.html)  
* [Whole Genome Resequencing (WGS)](POP_04_WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](POP_03_poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](POP_05_RDAtraitPredictionTutorial.html)
* [PCA](POP_08_PCA.html)
